\section*{\centering 摘要}
\vskip0.5cm
自区块链技术被确立为我国信息、科技领域的“顶层设计”，区块链作为核心技术的应用也愈发广泛。受新冠疫情的影响，线上教学在全国范围内迅速普及，一个交互好用、功能完备的线上考试系统作为线上教学的配套，十分重要。在2016年国家发布了《国家信息化发展战略纲要》，提倡要加强信息技术领域前沿的基础设施建设。因此，在这样的政策和社会背景下，借区块链技术不可篡改、可溯源的特性，所带来的数据安全方面的保障能力，提出了一种「基于区块链技术的考试系统」解决方案。项目旨在研究和解决如下几个方面的问题：

\begin{itemize}
    \item 线上教学环节中，使用在线考试系统来解决教学需要的测验的问题；
    \item 通过区块链技术保证集中化存储的考试数据不被篡改，有迹可循；
    \item 随机组卷保证了考卷的随机性，和考试的公平性；
    \item 自动改卷提高了学校、教育机构的教学工作的便捷性；
\end{itemize}

项目采用了前后端分离的解耦项目模型，其中前后端都采用了时下流行、成熟、经过企业级项目应用的检验的 SpringBoot 与 Vue，缩短了开发周期，保证了项目的稳定性。并且，使用新兴的国产区块链底层框架 Fisco Bcos，作为项目中区块链的技术实现，使得项目的数据管理对恶意攻击有一定的防御能力。以此，提供一个操作简易、交互友好且数据安全的线上考试系统，减轻老师工作流程中的负担，提高学校的管理效率。

\vspace*{1cm}

\textbf{关键词:} 区块链；Fisco Bcos；在线考试系统；SpringBoot；Vue
% \addcontentsline{toc}{section}{摘要}    % 目录中加入

\clearpage  % 分页

\section*{\centering \textbf{Abstract}}
\vskip0.5cm
Since blockchain technology has been established as the "top-level design" in China's information and technology fields, the application of blockchain as a core technology has become more and more widespread. Due to the impact of the new crown epidemic, online teaching is rapidly spreading across the country, and it is important to have an interactive and functional online examination system as a complement to online teaching. In 2016, the country released the "Outline of National Information Development Strategy", advocating the need to strengthen infrastructure construction at the forefront of information technology. Therefore, in such a policy and social context, a solution of "blockchain technology-based examination system" is proposed, taking advantage of the data security guarantee capability brought by the tamper-evident and traceable characteristics of blockchain technology. The project aims to study and solve problems in the following aspects:

\begin{itemize}
    \item Online teaching session using online examination system to solve the problem of quizzes needed for teaching;
    \item Using blockchain technology ensures that centrally stored exam data is not tampered with and can be traced;
    \item Random composition of papers ensures the randomness of the test and the fairness of the test
    \item Automatic paper correction improves the ease of teaching in schools and educational institutions;
\end{itemize}

The project adopts the decoupled project model of front-end and back-end separation, in which both front-end and back-end adopt SpringBoot and Vue, which are popular, mature and tested in enterprise-level projects, shortening the development cycle and ensuring the stability of the project. Moreover, we use the emerging domestic blockchain underlying framework Fisco Bcos as the technical implementation of blockchain in the project, so that the project data management has certain defense ability against malicious attacks. In this way, an easy-to-operate, interactive and data-secure online examination system is provided to reduce the burden of teachers in the workflow and improve the management efficiency of schools.

\vspace*{1cm}

\textbf{Key Words:} Block-chain; Fiscos Bcos; Online Exam-system; SpringBoot; Vue
% \addcontentsline{toc}{section}{Abstract}    % 目录中加入